\newpage
\section*{Saturday Session Descriptions}\label{saturday-descriptions}
\renewcommand{\conferenceDay}{\saturday}
\setPageBackground
% time: Saturday 09:30
% URL: https://pretalx.com/sotm2019/talk/HFET3E/

%
\newSmallTimeslot{09:30}
\abstractGHS{%
}{%
  Opening%
}{%
}{%
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 10:00
% URL: https://pretalx.com/sotm2019/talk/TWARHC/

%
\newSmallTimeslot{10:00}
\abstractGHS{%
  Dietmar Seifert, Christian Förster%
}{%
  \emph{Keynote} Open up! Why digital mobility needs participation%
}{%
}{%
  Baden-Württemberg’s Ministry of Transport aims at developing regional mobility data towards an
  open and interoperable framework for new mobility solutions~-- as part of a sustainable traffic
  system, realising efficiency, climate protection and living quality. On the way there, fair
  chances for innovation are key: Not only for better results but also for the involvement of most
  different societal actors. Cross-thinking and open innovation are cornerstones in such a process.%
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 10:30
% URL: https://pretalx.com/sotm2019/talk/VC8ESD/

%
\newSmallTimeslot{10:30}
\abstractGHS{%
  Karen M. Sandler%
}{%
  \emph{Keynote}%
}{%
}{%
  Karen M. Sandler is the executive director of the Software Freedom Conservancy, which is the
  non-profit home of dozens of free and open-source software projects including Git, Etherpad, QEMU,
  Selenium and Inkscape (to name but a few). She is known as a cyborg lawyer for her advocacy for free
  software as a life-or-death issue, particularly in relation to the software on medical devices.

%  Prior to joining the Conservancy, she was the executive director of the GNOME Foundation. Before
%  that, she was the general counsel of the Software Freedom Law Center.
  She co-organises
  Outreachy, the award-winning outreach programme for people who are subject to systemic bias and
  underrepresented in tech.
  Karen is an adjunct Lecturer-In-Law at Columbia Law School and a
  Visiting Scholar at UC Santa Cruz. She is the recipient of the Free Software Foundation's 2017
  Award for the Advancement of Free Software as well as an O'Reilly Open Source Award.
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 11:30
% URL: https://pretalx.com/sotm2019/talk/VZVFMS/

%
\newSmallTimeslot{11:30}
\abstractGHS{%
  Astrid Emde%
}{%
  Get to know OSGeo and how OSGeo is connected to OpenStreetMap%
}{%
  Open Source Software and Open Education making use of OSM data
}{%
  OSGeo is all about open-source software, open data and open education. Learn about OSGeo and what
  builds up this great organisation and find out how OpenStreetMap is used by OSGeo projects, how
  OSM can use OSGeo projects and how the two OSGeo and OSM are connected.%
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 11:30
% URL: https://pretalx.com/sotm2019/talk/7ZXRXB/

%

\abstractHSO{%
  Olivier Courtin \speakerAffiliation{DataPink}
}{%
  Data Quality and Feature Extraction at scale with RoboSat.pink%
}{%
}{%
  How to use plain open data and imagery to train an accurate deep learning model, able to detect
  inconsistencies in an OSM dataset, to spot it and to extract features.
  And make it work at scale, with an open-source solution named RoboSat.pink.%
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 11:30
% URL: https://pretalx.com/sotm2019/talk/NPYVSP/

%

\abstractHSW{%
  Thomas Skowron, Frederik Ramm%
}{%
  Introduction to OSM: How it's made and how it's used%
}{%
}{%
  This session provides an entertaining yet informative introduction into everything you need to
  know about OpenStreetMap.%
}


\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 11:30
% URL: https://pretalx.com/sotm2019/talk/Z9VBKM/


\abstractKHS{%
  Polyglot%
}{%
  Mapping public transport and cycling itineraries using JOSM's PT\_Assistant plugin~\noVideo %
}{%
}{%
  The PT\_Assistant plugin has been developed over the past 3 summers as a Google Summer of Code project and will
  probably see further development this summer. During this workshop, learn how
  PT\_Assistant can map itineraries for public transport, cycling and hiking.
  Bring a computer with Java installed on it to take part interactively.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 12:00
% URL: https://pretalx.com/sotm2019/talk/3WQKAX/

%
\newSmallTimeslot{12:00}
\abstractGHS{%
  Christopher Klaiber \speakerAffiliation{Facebook}, Kevin Ventullo \speakerAffiliation{Facebook}%
}{%
  ``Keepin' it fresh (and good)!''%
}{%
  Continuous Ingestion of OSM Data at Facebook%
}{%
  Building forward from our work on Mobius Logical Changesets (presented last year at SotM US 2018),
  we have created an automated ingestion framework for OSM data that allows us to selectively update
  parts of the map instead of doing a full snapshot change.%
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 12:00
% URL: https://pretalx.com/sotm2019/talk/KAPNKV/

%

\abstractHSO{%
  Christopher Beddow \speakerAffiliation{Mapillary}, Edoardo Neerhut \speakerAffiliation{Mapillary}%
}{%
  Human Mapping with Machine Data%
}{%
}{%
  How useful are map features automatically extracted from street-level images? Can they be trusted?
  These are some of the questions we tried to answer through community campaigns and student-led
  research in 2019. We will share some of these lessons and elicit a broader discussion on the
  methods that can be used to turn automatically extracted features into useful OpenStreetMap data.%
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 12:30
% URL: https://pretalx.com/sotm2019/talk/PAG8CN/

%
\newSmallTimeslot{12:30}
\abstractGHS{%
  Jinal Foflia \speakerAffiliation{Grab}%
}{%
  Driving South East Asia Forward with OpenStreetMap%
}{%
}{%
  It’s been more than a year since we at Grab incorporated OpenStreetMap into our ecosystem and we
  have come a long way since then. This talk will focus on our learning journey, our tools, the
  challenges and our experiences working in the South East Asia region and the vibrant OpenStreetMap
  communities here.%
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 12:30
% URL: https://pretalx.com/sotm2019/talk/DPGWFB/

%

\abstractHSO{%
  Felix Delattre \speakerAffiliation{HOT}, Surabhi Singh \speakerAffiliation{Microsoft/HOT}%
}{%
  Assisted Intelligence~-- How we map with the support of new technologies%
}{%
}{%
  Deep learning methods for feature extraction using computer vision are giving concrete results.
  This talk provides an overview of feature detection from satellite imagery and how machine
  learning can provide a seamless mapping experience for mappers, allowing them to utilise their
  knowledge to enrich maps further.%
}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 14:30
% URL: https://pretalx.com/sotm2019/talk/UN33XK/

%
\newSmallTimeslot{14:30}
\abstractGHS{%
  Kathleen Lu \speakerAffiliation{LWG}%
}{%
  ODbL licence compatibility%
}{%
}{%
  Have you ever wondered if a certain dataset can be used for OSM? What does it mean for a licence to be
  ``compatible'' with OSM and ODbL? This talk will give pointers on where to look for information,
  common compatibility issues, and best practices for presenting a licence to the Licensing Working Group (LWG) for help review.%
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 14:30
% URL: https://pretalx.com/sotm2019/talk/FLPYCN/

%

\abstractHSO{%
}{%
  Lightning Talks I%
}{%
}{%
  %TODO adapt space
  \vspace{-1.5em}
  \begin{itemize}
    \RaggedRight
    \setlength{\itemsep}{-3pt} % Aufzählungspunktabstand auf 0
    \lightningTalk{Uses of native language in OSM}{S M Sawan Shariar \speakerAffiliation{YouthMappers Dhaka College}}
    \lightningTalk{SolidaryCityMap}{OpenDEM}
    \lightningTalk{OpenLitterMap~-- open data on plastic pollution with blockchain rewards (Littercoin)}{Seán Lynch \speakerAffiliation{OpenLitterMap}}
    \lightningTalk{Map2endFGM}{Janet Chapman \speakerAffiliation{Crowd2Map Tanzania}}
  \end{itemize}%
  \justifying
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 14:30
% URL: https://pretalx.com/sotm2019/talk/N9RCV8/


\abstractHSW{%
  Roland Olbricht%
}{%
  Share Edits and Insights with the Overpass Tools%
}{%
}{%
  Not every data item in OpenStreetMap can have an immediate impact on the rendered map. But you can
  make every data item visible on a map and share the links or share the data, no matter how much
  the item is special interest. This is the purpose of Overpass API and Overpass Turbo.%
}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% time: Saturday 14:30
% URL: https://pretalx.com/sotm2019/talk/JJUFQT/


\abstractKHS{%
  Manfred Reiter%
}{%
  How to contribute to weeklyOSM via the CMS~-- OSMBC~\noVideo%
}{%
  The OSM community should know about it~\dots%
}{%
  OSMBC is the Content Management System to produce weeklyOSM in recently nine languages.%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 15:00
% URL: https://pretalx.com/sotm2019/talk/R3BAWM/

%
\newSmallTimeslot{15:00}
\abstractGHS{%
  Hanna Krüger%
}{%
  Communication and Knowledge Transfer in OpenStreetMap%
}{%
}{%
  The OpenStreetMap project uses many different technologies and channels for communication and documentation. This talk is an overview of various communication platforms and their relevance and reach at local and international level. In addition, the advantages and disadvantages of the current strategy for communication and knowledge transfer will be discussed.
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 15:00
% URL: https://pretalx.com/sotm2019/talk/VAADJ9/

%

\abstractHSO{%
  Thomas Sontag, Andreas Dirks, Hannes Geißelmann, Adrien Pavie%
}{%
  OsmInEdit: a simple indoor editor%
}{%
}{%
  The Indoor Map Creator is an easy-to-use open-source map editor for OSM indoor data. It is
  web-based with an intuitive user interface to make mapping indoors accessible and easy for
  everyone. Check it out and enjoy mapping buildings!%
}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 15:30
% URL: https://pretalx.com/sotm2019/talk/FAGNLA/

%
\newSmallTimeslot{15:30}
\abstractGHS{%
  Michael Spreng%
}{%
  Past and Future of the OSMF Membership Working Group%
}{%
}{%
  What is an OSMF working group? What does the membership working group in particular do? And how
  can you improve the experience of an OSMF membership?%
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 15:30
% URL: https://pretalx.com/sotm2019/talk/39SBT8/
%

\enlargethispage{1\baselineskip}

\abstractHSO{%
  Sajjad Anwar%
}{%
  Observe~-- offline, cross-platform field mapping tool for OpenStreetMap%
}{%
}{%
  Over the last few months, we’ve been building an offline-first field mapping tool for the
  OSM ecosystem called Observe. Observe makes field surveying and verification easy for
  mappers, and works on iOS and Android. My talk will cover how Observe integrates with mapping
  workflows and helps improve OSM data from the field. I'll also touch upon fundamentals of building
  Observe and our assumptions on field mapping.%
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 16:30
% URL: https://pretalx.com/sotm2019/talk/799WZF/

%
\newSmallTimeslot{16:30}
\abstractGHS{%
  Yantisa Akhadi \speakerAffiliation{HOT}%
}{%
  OSM Data: From Digital to Physical Design%
}{%
}{%
  Exploring the visualisation of OSM data outside its digital form and how it can be applied to
  everyday objects from book covers to wallpaper. This talk will discuss how to elevate OSM data
  beyond maps, exploring its potential in data-as-decor in both public and private space. The talk
  will describe the tools and workflow used to create these products as well as its strengths and
  weaknesses.%
}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% time: Saturday 16:30
% URL: https://pretalx.com/sotm2019/talk/BBRMPZ/

%

\abstractHSO{%
}{%
  Lightning Talks II%
}{%
}{%
  %TODO adapt space
  \vspace{-1em}
  \begin{itemize}
    \RaggedRight
    \setlength{\itemsep}{-3pt} % Aufzählungspunktabstand auf 0
    \lightningTalk{OpenStreetMap intrinsic quality assessment using ``Is OSM up-to-date?'' web application}{Marco Minghini, Francesco Frassinelli}
    \lightningTalk{Deriviste~-- Click and Go Photo Mapping}{Christopher Beddow \speakerAffiliation{Mapillary}}
    \lightningTalk{Fifty states in 12 years and five minutes}{Minh Nguyễn}
    \lightningTalk{``MAPAbabae'': Using OSM as a Tool for Mapping with Women and For Women}{Andi Tabinas, Arnalie Vicario}
    \lightningTalk{Reverse Geocoding Is Not Simple}{Ilya Zverev}
  \end{itemize}%
  \justifying
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 16:30
% URL: https://pretalx.com/sotm2019/talk/9MR9QK/

%

\abstractHSW{%
  Joost Schouppe \speakerAffiliation{OSMF}%
}{%
  OSMF Board + Working Groups meeting%
}{%
}{%
  Get to know the Board and the Working Groups. Together, we run the OSMF. Let's use the SotM to
  have a real face-to-face meeting. The public is invited to join the conversation too.%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 16:30
% URL: https://pretalx.com/sotm2019/talk/J7D7UU/


\abstractKHS{%
  Manfred Reiter%
}{%
  uMap for newbies~\noVideo%
}{%
}{%
  We create an individualised map based on OSM using uMap.%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 17:00
% URL: https://pretalx.com/sotm2019/talk/SBDEU8/

%
\newSmallTimeslot{17:00}
\abstractGHS{%
  Florimond Berthoux, Lucas Verney%
}{%
  CyclOSM, a bicycle oriented render for every cyclist%
}{%
}{%
  CyclOSM is a new cycling render. It is free and aims at rendering new bicycle-specific features,
  in order to take into account the diversity of cycling practices.%
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 17:00
% URL: https://pretalx.com/sotm2019/talk/9TMRYN/

%

\abstractHSO{%
  Robert Kaiser \speakerAffiliation{Mozilla}%
}{%
  VR Map: Using OSM Data In a WebVR Environment%
}{%
  Simple GeoData Visualisation with A-Frame
}{%
  Can you actually walk through or fly over a 3D scene of live OSM data using a VR headset?~-- and if
  so, can this be done in a way that easily transforms to a view on a normal computer (or mobile)
  screen?
  The answers are ``Yes'' and ``Yes'', and this talk will show how this can be done with relatively
  simple code, and all inside a web browser!%
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 17:30
% URL: https://pretalx.com/sotm2019/talk/JNXE9Q/

%
\newSmallTimeslot{17:30}
\abstractGHS{%
  Astrid Emde \speakerAffiliation{OSGeo}%
}{%
  How to Use OpenStreetMap Data with the Desktop GIS QGIS%
}{%
  Get to Know the Great Combination of OSM Data and QGIS%
}{%
  The desktop GIS QGIS offers many ways to work with OSM data. This presentation will give
  an overview on how you can use OSM data with QGIS.%
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% time: Saturday 17:30
% URL: https://pretalx.com/sotm2019/talk/DETEML/

%

\abstractHSO{%
  Nick Whitelegg \speakerAffiliation{Solent University}%
}{%
  Hikar~-- OSM Augmented Reality for Walkers across Europe%
}{%
}{%
  Hikar is an OSM-based augmented reality navigation app for walkers and hikers, showing OSM ways
  overlaid on the camera feed of the device and, in the latest version, virtual signposts pointing
  the way to nearby points of interest. This technical talk will introduce Hikar, detail the many
  new developments since it was last presented at SotM Birmingham 2013, and describe how it works in
  technical detail.%
}

\enlargethispage{2\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newSmallTimeslot{19:00}
\abstractOther{%
}{%
  Social Event%
}{%
}{%
  See page~\pageref{social-event} for details about the social event.
}{%
  Hebelhalle%
}
